% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black 
    %urlcolor=mygreylink     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.40}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubsubheading}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textit{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{\href{http://www.ashish-jindal.com/}{\LARGE Ashish Jindal}} & {\footnotesize \texttt{(848) 237-9929}}\\
	{\footnotesize \texttt{23 James St}} & {\footnotesize \texttt{\href{mailto:ashish.jindal@rutgers.edu}{ashish.jindal@rutgers.edu}}}\\
	 {\footnotesize \texttt{New Brunswick, NJ 08901}} & {\footnotesize \texttt{\href{http://www.ashish-jindal.com/}{http://ashish-jindal.com/}}} \\
	\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
	\begin{itemize}
		\item
			\ressubheading{\href{http://www.rutgers.edu/}{Rutgers University - New Brunswick}}{New Jersey, US}{\href{https://www.cs.rutgers.edu/}{MS in Computer Science}; \href{http://www.ashish-jindal.com/rutgers_unofficial_transcript.pdf}{GPA : 4.0}}{Aug, 2015 -- May, 2017}
				{ \footnotesize
				\begin{itemize}
					%\resitem{\textbf{Available for internship: July 23, 2009; Graduation follows internship}}
					\resitem{Key Courses: \href{https://www.cs.rutgers.edu/graduate/courses/512/}{Data Structures and Algorithms}, \href{https://www.cs.rutgers.edu/graduate/courses/518/}{Operating Systems Design}, \href{https://www.cs.rutgers.edu/graduate/courses/539/}{Database Systems Implementation}.}
				\end{itemize}
				}
	\end{itemize}
	
	\begin{itemize}
		\item
			\ressubheading{\href{http://www.nith.ac.in/}{National Institute of Technology - Hamirpur}}{Himachal Pradesh, India}{\href{http://www.nith.ac.in/ece/}{B.Tech. in Electronics and Communication Engineering}; \href{http://www.ashish-jindal.com/nith_unofficial_transcript.pdf}{CGPI : 7.83}}{Aug, 2008 -- May, 2012}
				{ \footnotesize
				\begin{itemize}
					%\resitem{\textbf{Available for internship: July 23, 2009; Graduation follows internship}}
					\resitem{Key Courses: Digital Electronics and Logic Design, Data Structures, Microprocessors, Micro-Controllers and Embedded System Design, Mobile Communication, Differential Equations and Probability.}
					
				\end{itemize}
				}
	\end{itemize} % End Education list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Work Experience}
	\begin{itemize}
		\item 
			\ressubheading{\href{http://www.nagarro.com/}{Nagarro}}{Gurgaon, India}
				{Windows based accounting software}{Jul, 2012 -- Jun, 2014}
				{ \footnotesize
				\begin{itemize}
					\resitem{Implemented front end application components - Navigation bar, Title bar, Buttons, Dialogs, MDI windows etc. using WIN32 and MFC as per UX team requirements.}
					\resitem{Independently revamped many legacy features in application's code. One of the major ones was a WIN32 based custom control called Quickfill.}
					\resitem{Worked on PoC tasks in the application leading to major feature upgrades. Application's navigation bar was one such major contribution from my side.}
					\resitem{Analysed the code for budget feature of the application and prepared the design for its revamped version.}
				\end{itemize}
				}

			\ressubsubheading{Fleet Distribution System}{Jul, 2014 -- Sep, 2014}
				{ \footnotesize
				\begin{itemize}
					\resitem{Ported the server side C++ code from x-86 to x-64 architecture.}
					\resitem{Implemented an application to automate the log analysis process for the QA team.}
				\end{itemize}
				}

			\ressubsubheading{Web based Supply chain management system}{Jan, 2015 -- Jul, 2015}
				{ \footnotesize
				\begin{itemize}
					\resitem{Implemented data export in Excel format using Apache poi.}
					\resitem{Resolved application defect incidents reported by customers.}
					\resitem{Worked with product owner's development team for implementing new features into the application.}
				\end{itemize}
				}				
	\end{itemize}  % End Experience list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{\href{http://www.ashish-jindal.com/}{Skills}}
	\begin{description}
		\item[Languages:] { \footnotesize C (Proficient), C++ (Intermediate), Java (Intermediate), HTML (Proficient), CSS (Intermediate), JavaScript (Beginner), SQL (Beginner)
		}
		\item[Technologies:] { \footnotesize
			MongoDB (Beginner), SpringMVC (Intermediate), Hibernate (Intermediate), Spring Security (Beginner), Apache Tiles (Beginner), Bootstrap (Intermediate), Hadoop (Beginner), AWS [S3, EMR, EC2] (Beginner)
		}

	\end{description} % End Skills list

\resheading{\href{http://www.ashish-jindal.com/}{Projects}}

\begin{description}
\item[Linux Scheduler:] { \footnotesize Implemented multi level feedback queues based scheduler in Linux kernel 2.4 and compared its performance with the older O(n) scheduler.}

\item[UFS based File System:] { \footnotesize Implemented a basic version of Unix File System using Fuse module; which supports create/delete/read/write of files using direct indexing and also supports mkdir/rm/ls on directory entries.}

\item[Wikipedia data analysis using Hadoop:] { \footnotesize Analysis of Wikipedia page popularity trends using a simple baseline algorithm and comparison of relative page ranks of various Wiki pages using Map-Reduce. Nominated as best project in class.}
\end{description}

\resheading{\href{http://www.ashish-jindal.com/}{Awards}}

\begin{description}
\item[Most Promising Fresher:] { \footnotesize Received this award from my employer - Nagarro, as an appreciation for gaining project domain knowledge in a short period of time..}

\end{description}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%
% GENERAL RESUME NOTES %
%%%%%%%%%%%%%%%%%%%%%%%%
Need to brush up on the skills section?  Here are some really good ideas:

- Communication: The ability to express and interpret ideas and convey knowledge. 
Skills like speaking effectively, writing concisely, listening attentively, expressing ideas, 
reporting information, editing, interviewing, and facilitating group discussion. 
 
- Research and Planning: The ability to search for specific knowledge and formulate a 
program for a definite course of action. Skills like forecasting, predicting, identifying 
issues, finding alternatives, gathering information, solving problems, setting goals, 
extracting information, and developing strategies. 
 
- Human Relations: The ability to apply interpersonal skills to resolve conflict, relate to 
people, and help people. Skills like providing support for others, listening, delegating 
with respect, representing others, asserting, developing rapport, and perceiving 
feelings. 
 
- Management, Organization, Leadership: The ability to supervise others and guide 
individuals and groups towards the completion of tasks. Skills like managing groups, 
selling ideas, making decisions, managing conflict, coordinating tasks, teaching, 
enlisting help. 

Source: 
http://www.squawkfox.com/2009/03/08/6-action-words-that-make-your-resume-rock/

Other Resources: 
http://www.tvmier.com/Resume_Education.html

