% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black 
    %urlcolor=mygreylink     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.40}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubsubheading}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textit{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{\href{http://www.ashish-jindal.com/}{\LARGE Ashish Jindal}} & {\footnotesize \texttt{(848) 237-9929}}\\
	{\footnotesize \texttt{23 James St}} & {\footnotesize \texttt{\href{mailto:ashishj1707@gmail.com}{ashishj1707@gmail.com}}}\\
	 {\footnotesize \texttt{New Brunswick NJ 08901}} & {\footnotesize \texttt{\href{http://www.ashish-jindal.com/}{http://ashish-jindal.com/}}} \\
	\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
	\begin{itemize}
		\item
			\ressubheading{\href{http://www.rutgers.edu/}{Rutgers University - New Brunswick}}{New Jersey, US}{\href{https://www.cs.rutgers.edu/}{MS in Computer Science}; \href{http://www.ashish-jindal.com/rutgers_unofficial_transcript.pdf}{GPA : 4.0}}{Aug. 2015 -- May. 2017}
				{ \footnotesize
				\begin{itemize}
					%\resitem{\textbf{Available for internship: July 23, 2009; Graduation follows internship}}
					\resitem{Key Courses: \href{https://www.cs.rutgers.edu/graduate/courses/512/}{Data structures and Algorithms}, \href{https://www.cs.rutgers.edu/graduate/courses/518/}{Operating Systems design}, \href{https://www.cs.rutgers.edu/graduate/courses/539/}{Database Systems Implementation}}
				\end{itemize}
				}
	\end{itemize}
	
	\begin{itemize}
		\item
			\ressubheading{\href{http://www.nith.ac.in/}{National Institute of Technology - Hamirpur}}{Himachal Pradesh, India}{\href{http://www.nith.ac.in/ece/}{B.Tech. in Electronics and Communication Engineering}; \href{http://www.ashish-jindal.com/nith_unofficial_transcript.pdf}{CGPI : 7.83}}{Aug. 2008 -- May. 2012}
				{ \footnotesize
				\begin{itemize}
					%\resitem{\textbf{Available for internship: July 23, 2009; Graduation follows internship}}
					\resitem{Key Courses: Digital electronics and Logic Design, Data Structures, Microprocessors, Micro-controllers and Embedded System design, Mobile Communication, Differential equations and Probability}
					
				\end{itemize}
				}
	\end{itemize} % End Education list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
	\begin{itemize}
		\item 
			\ressubheading{\href{http://www.nagarro.com/}{Nagarro Softwares pvt. ltd.}}{Gurgaon, India}
				{Quicken: Accounting Software by Lexware}{Jul. 2012 -- Jun. 2014}
				{ \footnotesize
				\begin{itemize}
					\resitem{Implemented front end application components - Navigation bar, Title bar, Buttons, Dialogs, MDI windows etc. using WIN32 and MFC as per UX team requirements.}
					\resitem{Independently revamped many legacy features in application's code. One of the major one's was a WIN32 based custom control called Quickfill.}
					\resitem{Worked on many poc tasks in the application leading to major feature upgrades. Application's navigation bar was one such major contribution from my side.}
					\resitem{Analysed the code for budget feature of the application and prepared the design for its revamped version.}
				\end{itemize}
				}

			\ressubsubheading{UFD: Unified Freight Distribution System by TTX}{Jul. 2014 -- Sep. 2014}
				{ \footnotesize
				\begin{itemize}
					\resitem{Ported the server side C++ code from x-86 to x-64 architecture}
					\resitem{Reduced the build time of the project from 1.5 hours to 30 minutes; by tuning project settings like pre-
compiled headers, build output verbosity, compiler optimization settings etc.}
					\resitem{Implemented an application to automate the log analysis process for the QA team.}
				\end{itemize}
				}

			\ressubsubheading{CAP Webapp: Web application for College of American Pathologists}{Dec. 2014 -- Jul. 2015}
				{ \footnotesize
				\begin{itemize}
					\resitem{Analysed user requirements and provided development estimations to product owner.}
					\resitem{Worked with product owner's development team for implementing new features into the application.}
					\end{itemize}
				}			

			\ressubsubheading{LDrive: Web based Supply chain management system for Lufthansa}{Mar. 2015 -- Jul. 2015}
				{ \footnotesize
				\begin{itemize}
					\resitem{Implemented data export in Excel format using Apache poi.}
					\resitem{Resolved application defect incidents reported by customers.}
				\end{itemize}
				}
	\end{itemize}  % End Experience list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{\href{http://www.ashish-jindal.com/}{Skills}}
	\begin{description}
		\item[Languages:] { \footnotesize C (Proficient), C++ (Intermediate), Java (Intermediate), HTML (Proficient), CSS (Intermediate), JavaScript (Beginner), SQL (Beginner)
		}
		\item[Technologies:] { \footnotesize
			MongoDB (Beginner), SpringMVC (Intermediate), Hibernate (Intermediate), Spring Security (Beginner), Apache Tiles (Beginner), Hadoop (Beginner), AWS [S3, EMR, EC2] (Beginner)
		}

	\end{description} % End Skills list

\resheading{\href{http://www.ashish-jindal.com/}{Projects}}

\begin{description}
\item[Pydom:] { \footnotesize Pydom scans through a list of web pages, grabs the HTML source, and parses interactive elements. These interactive elements written to an XML catalog which is used as the main input for a Selenium .Net project.}

\item[Xerrscrape:] { \footnotesize Used to fill a missing area of product testing, this Python program scans through all XML error logs on the specified server, tallies errors collectively, and sends notifications when an error occurs more than the threshold.}

\item[.Net CWS Test API:] { \footnotesize This framework provides automated testing for RightNow Connect Web Services for SOAP (.Net Toolkit).  Using reflection, objects and NUnit tests are instantiated based on JSON input.}
\item[\href{https://bitbucket.org/dhildreth/canon\_webview}{Canon Webcam API}:] {\footnotesize Allows programmatic authentication and control for Canon 360$^\circ$ Webcams in Python.}
\end{description}

\end{document}


%%%%%%%%%%%%%%%%%%%%%%
% Would have completed this if I had not had all projects listed under "Skills".  
% Still a good idea.  See if I can fit it in somewhere...  Otherwise, just print it out and bring it to an interview if needed.
%%%%%%%%%%%%%%%%%%%%%%
\newpage
\myheader
\resheading{Hardware Engineering Projects} % If printed as a seperate page, get more detailed in the descriptions!  What type of processor?  What program used? Etc.
	
	\begin{description}
		\item[4 and 8 bit RISC CPUs] {\footnotesize Simple CPUs designed using CircuitMaker (no HDL) which contained ALUs, counters, registers, and 1K RAM all designed from scratch}
		\item[Simple Calculator] {\footnotesize Designed a simple calculator from the ground up using Xilinx ISE and Verilog HDL} % Get schematic block diagram for this one!
		\item[Stereo Amplifier] {\footnotesize Contained I/O as well as bass, treble, and volume controls}
		\item[Power Supply Basics] {\footnotesize Learned about the very basics of power supply design using transformers, rectifiers, and zener diodes and voltage regulators.} 
		\item[Parallel Port Game Controller] {\footnotesize Went through the start to finish development process of a game controller including driver development, microprocessor  \& ADC design (8255 MicroBoard; N.I.	ADC0809), and PCB design}
		\item[Portable Microphone Amplifier] {\footnotesize Utilized a series of transistors to amplify sound in a room with a potentiometer as volume control}
		\item[MP3 Player] {\footnotesize Developed an MP3 player using the Analog Devices BlackFin BF533 microprocessor and EZ-KIT development kit which utilized interrupts and audio codec}  % get link to block diagram for this one!
		\item[INL Remote Cell Phone Control] {\footnotesize Senior project which developed a prototype for Idaho National Laboratories allowing them to remote control a cell phone via 802.11g and bluetooth at a range greater than 6000ft consisting of 3 major components: central control, wireless medium, and embedded systems for chuckar box}
		\item[Inverted Pendulum] {\footnotesize Used sliding mode feedback control and inverted pendulum kit to keep metal rod standing vertially on a swingin arm}
		\item[FM Transmitter] {\footnotesize Built a simple FM Transmitter based off of given schematics as an introduction to FM modulation signals}
	\end{description}


\resheading{Software Engineering Projects}  % There really are a TON of projects I can put on this, but here are some major ones:
	\begin{description}
		\item[Book Keyword Scanner] {\footnotesize Developed a program which will take any input file and, given a keyword search, will return the frequency of that word }
		\item[Pedigree Chart] {\footnotesize Developed a program which will parse through a pedigree file and display a pedigree chart in the command line}
		\item[Factory Nail Rejection] {\footnotesize This program was simulating a factory which produced nails that had to be a very specific length, and if it wasn't, the program would reject it}
		\item[Calendar Program] {\footnotesize Given the time and date to display, the calendar program would display a simple calendar on the command line which took into account leap years}
		\item[Normal Distribution] {\footnotesize This program simulated the classic wheel of fortune blinko game where several thousand chip were statistially recorded and displayed as they dropped into a board filled with pegs}
		\item[RSA Encryption] {\footnotesize Developed an application which utilized the RSA encryption method to encrypt and decrypt messages}
	\end{description}

\end{document}

%Only Print References If Requested!  Maybe even put it in it's own page.  Must have same heading as first page.
%%%%%%%%%%%%%%%%%%%%%%
\newpage
\myheader
\resheading{References}
	\begin{center}
		\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}  l l l }
			Toby Rummans & Eric Karl & Gordon Smith \\
			Entry Level Web Developer & Computer Science \& Engineering  & Technology Support Specialist \\ 
			\vspace{10pt} 
			Memolinkcorp & BYU-Idaho & BYU-Idaho \\ 
			[removed] & 525 South Center St. & 525 South Center St.  \\
			Denver, CO 80210 & Rexburg ID 83460 & Rexburg ID 83460 \\
			[removed] & (208) 496-3097 & (208) 496-2816 \\
		\end{tabular*}
	\end{center}
	
% \end{document}


% ADDITIONAL WORK EXPERIENCE NOT INCLUDED	OR OLD

		\item 
			\ressubheading{\href{http://www.rexburgmotorsports.com/}{Rexburg Motorsports}}{Rexburg, ID}{Computer Systems Administrator}{Aug. 2006 -- Oct. 2006}
				{ \footnotesize
				\begin{itemize}
	            			\resitem{Managed file and application servers running Windows 2003 Server}
	            			\resitem{Performed all levels of hardware and software systems support for 40 computers and 10 printers}
				\end{itemize}
				}

		\item 
			\ressubheading{Bresnan Communications}{Billings, MT}{Teir 1 Technical Support}{Jan. 2006 -- April 2006}
				{ \footnotesize
				\begin{itemize}
					\resitem{Provided Bresnan customers with technical support over the phone.}
					\resitem{Receieved training on resolving networking, cable TV, and VOIP issues.}
				\end{itemize}
				}

		\item 
			\ressubheading{Northwestern Energy}{Billings, MT}{Summer Gas/Electrical Engineer}{May 2004 -- April 2005}
				\begin{itemize}
					\resitem{Interned with full time Gas/Electrical Engineers.}
					\resitem{Documented, mapped, and marked city streetlights using MS Access, GTViewer, FRAMME, and CAD.}
				\end{itemize} 


%%%%%%%%%%%%%%%%%%%%%%%%
% GENERAL RESUME NOTES %
%%%%%%%%%%%%%%%%%%%%%%%%
Need to brush up on the skills section?  Here are some really good ideas:

- Communication: The ability to express and interpret ideas and convey knowledge. 
Skills like speaking effectively, writing concisely, listening attentively, expressing ideas, 
reporting information, editing, interviewing, and facilitating group discussion. 
 
- Research and Planning: The ability to search for specific knowledge and formulate a 
program for a definite course of action. Skills like forecasting, predicting, identifying 
issues, finding alternatives, gathering information, solving problems, setting goals, 
extracting information, and developing strategies. 
 
- Human Relations: The ability to apply interpersonal skills to resolve conflict, relate to 
people, and help people. Skills like providing support for others, listening, delegating 
with respect, representing others, asserting, developing rapport, and perceiving 
feelings. 
 
- Management, Organization, Leadership: The ability to supervise others and guide 
individuals and groups towards the completion of tasks. Skills like managing groups, 
selling ideas, making decisions, managing conflict, coordinating tasks, teaching, 
enlisting help. 

Source: 
http://www.squawkfox.com/2009/03/08/6-action-words-that-make-your-resume-rock/

Other Resources: 
http://www.tvmier.com/Resume_Education.html

